Increasing productivity amid stable nutrient regmines in Rhode Island Lakes and Reservoirs

### 2019-11-08 nalms_2019_talk/increasing_chla_stable_nutrients_talk.Rmd
slides in Rmd done - future edits to pptx

@@

## URI Watersehd Watch: Lake Sampling

@@

@@

## Analysis: Site-specific z-scores

@@

## Analysis: Yearly trends

@@

@@

@@

@@

@@

### Within the Northeast
- Stasis (our analysis concurs)

@@

>>>>

![](figures/green_lake.png)

![](figures/not_green_lake.png)

@@

![](figures/WW-Logo1.gif)
## URI Watersehd Watch: Lake Sampling

@@

![](figures/boy-w-tube_EH.jpg)

![](figures/14 V lowering deep sampler_EH.jpg)

@@

## Analysis: Site-specific z-scores and yearly trends

- Calculate average yearly z-score
- Look for monotonic yearly trend
  - Slope of regression line

@@

@@

- RI: Increasing but driven by low years in 1993 and 1994
  - Without those years slope = 0.01 and p-value = 0.06
- LAGOSNE: Static

@@

- RI: Static
- LAGOSNE: Static

@@

- RI: Increasing
- LAGOSNE: Static

@@

- RI: Increasing
- LAGOSNE: NA

@@

### Within the Northeast
- Stasis
  - Our results concur with Oliver et al. (2017)

@@

![](figures/yawgoo.jpg)
